### 2021-07-22 doc/thesis/chapters/deployment-on-hardware.tex
software

The application software is running on a single core of the dual-core ARM Cortex A9 CPU and is built upon a real-time operating system, namely FreeRTOS.
Xilinx provides a ported version of this RTOS with the installation of their software development kit, the Xilinx SDK.
The SDK also includes drivers to support various functionalities, such as support for accessing a FAT file system on the external SD card.
The respective software drivers for the IPs that are used in the FPGA design are automatically imported into the SDK project.
They are embedded in the so-called hardware definition file (HDF) that is generated by Vivado after synthesis, and provided together with the bitstream file.
It is a file with the extension \textit{*.hdf} and can be opened like a regular archive file, with any ZIP archive viewer.

\texttt{--->} look at software which parts may be interesting to highlight

>>>>

The application software is running on a single core of the dual-core ARM Cortex A9 CPU and is built upon a real-time operating system, namely FreeRTOS.
Xilinx provides a ported version of this RTOS with the installation of their software development kit, the Xilinx SDK.
The SDK also includes drivers to support various functionalities, such as support for accessing a FAT file system on the external SD card.\\

The respective software drivers for several IPs that are used in the FPGA design are automatically imported into the SDK project.
They are embedded in the so-called hardware definition file (HDF) that is generated by Vivado after the synthesis process, and provided together with the bitstream file.
It is a file with the extension \textit{*.hdf} and can be opened like a regular archive file, with any ZIP archive viewer.\\

Generally, the application software for this project is developed as an object-oriented \cplusplus\ program.
It uses common software development patterns and a class structure that fits the purpose.
The main tasks of the application are to configure several IPs in the FPGA, so that they can fulfill their respective purpose in the system, and to read the recorded data from the SD card, which is then streamed to the FPGA.
It also provides a basic user interface over the serial console, with which a user can interact with the FM Radio Receiver product.\\

However, software design is not the main focus of this thesis, and thus no further details are discussed here.
